Keep your Laziness in Check

### 2018-01-18 paper/main.tex
fixing Kenny's name
push comments from Tuesday's comments

%% Author with single affiliation.
\author{Kenneth Fonner}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
%  \department{Department1}              %% \department is recommended
  \institution{University of Pennsylvania}            %% \institution is required
%  \streetaddress{Street1 Address1}
%  \city{City1}
%  \state{State1}
%  \postcode{Post-Code1}
  \country{USA}
}
\email{kwf@very.science}          %% \email is recommended

@@

\hzh{Rewrite counter: 1}
\leo{I want to keep a counter on how many times we'll rewrite this intro :)}

@@

However, using \lk{foldl'} is not sufficient to avoid space leaks in
general. Consider a single-traversal computation of an average where we keep
both a running sum and a running counter in an accumulator.
%
\begin{inlinecode}
avg = uncurry (/) . foldl (\(s,n) x -> (s + x, n + 1)) (0,0)
\end{inlinecode}
%
In this case, both \lk{foldl} and \lk{foldl'} construct thunks linear in the
size of the input list, since forcing a lazy pair only evaluates it to its weak
head normal form, and it does not evaluate either component of the pair.

@@

Our technical contributions are as follows:
\begin{itemize}
\item We introduce a novel approach to specifying the laziness behavior of functions that is
{\em precise}. Such specifications are expressive enough to capture exactly how
much evaluation occurs within a data structure \leo{Also add
drawbacks/partiality here? If not here, where in the intro?} \hzh{I'm not sure
if we should bring in partiality (in the sense of divergence/nontermination) yet
since that seems like a rather technical detail of the spec}
\item We propose a framework for testing against such specifications.
\item We improve upon the random function generators from QuickCheck to generate functions with arbitrary laziness behaviors.
\item We demonstrate non-trivial generic programming techniques to apply StrictCheck to almost all data types.
\end{itemize}
%
Section~\ref{sec:related} discusses related work. We conclude and draw
directions for future work in Section~\ref{sec:concl}.

>>>>

%% Author with single affiliation.
\author{Kenneth Foner}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
%  \department{Department1}              %% \department is recommended
  \institution{University of Pennsylvania}            %% \institution is required
%  \streetaddress{Street1 Address1}
%  \city{City1}
%  \state{State1}
%  \postcode{Post-Code1}
  \country{USA}
}
\email{kfoner@seas.upenn.edu}          %% \email is recommended

@@

\hzh{Rewrite counter: 1}
\hzh{Rewrite the intro using different running examples, foldl vs foldr on stream manipulations?}
\hzh{We can write a hand-crafted spec for take, can we show that we can create this spec by composing the spec for foldr (but not using the one with foldl)}
\hzh{implement take in 3 ways: foldl, foldr and explicitly as the opening example, and then ask if they're equivalent? (they're not!)}
\hzh{Okasaki has 2 functions that appends a list to the reversal of another list, one of which is too strict and the other one is just the right amount of lazy (thus incremental)}
\hzh{The amortized one is hard to specify exactly, but we can introduce approximate specification and specify it approximately}
\hzh{we need to carefully avoid saying this is a tool for specifying the time complexity of functions}
\hzh{Implementing functional programs that make clever use of laziness is very easy to get wrong, and we provide a solution to make sure the programmer got it right. We almost have no way of testing it right now before StrictCheck.}
\hzh{Email Ryan Trinkle and Dan Winograd-Cort about FRP and strictness, and try to use their examples as another problem we can solve in the intro}
\hzh{Lazy maps will mess up memoization if you're overly strict, use knapsack as an example}
\leo{I want to keep a counter on how many times we'll rewrite this intro :)}

@@

However, using \lk{foldl'} is not sufficient to avoid space leaks in
general. Consider a single-traversal computation of an average where we keep
both a running sum and a running counter in an accumulator.
%
\hzh{TODO: rewrite this, let bind the foldl}
\begin{inlinecode}
avg = uncurry (/) . foldl (\(s,n) x -> (s + x, n + 1)) (0,0)
\end{inlinecode}
%
In this case, both \lk{foldl} and \lk{foldl'} construct thunks linear in the
size of the input list, since forcing a lazy pair only evaluates it to its weak
head normal form, and it does not evaluate either component of the pair.

@@

Our technical contributions are as follows:
\begin{itemize}
\item We introduce a novel approach to specifying the laziness behavior of functions that is
{\em precise} \hzh{and compositional}. Such specifications are
expressive enough to capture exactly how much evaluation occurs within
a data structure \leo{Also add drawbacks/partiality here? If not here,
where in the intro?} \hzh{I'm not sure if we should bring in
partiality (in the sense of divergence/nontermination) yet since that
seems like a rather technical detail of the spec}
\item We propose a framework for testing against such specifications.
\item We improve upon the random function generators from QuickCheck to generate functions with arbitrary laziness behaviors.
\item We demonstrate non-trivial generic programming techniques to apply StrictCheck to almost all data types.
\end{itemize}
%
Section~\ref{sec:related} discusses related work. We conclude and draw
directions for future work in Section~\ref{sec:concl}.
